RAS2012: Competition Entry

### 2012-07-27 ras2012-paper/src/main/latex/paper/paper.tex
Adding the introductory bits.

\begin{abstract}
This article describes an entry to the 2012 RAS Problem Solving Competition, concerning dispatching on multi-track territories. The entry is based on the Drools Planner, a Java-based solver. On a reasonably recent computer, the resulting algorithm is able to produce feasible results within a minute and has been fine-tuned to provide best results in under 3 minutes. Source code of the entry is open and well documented.
\end{abstract}

@@

@@

In this section, we will describe the various approaches we have taken to implement the rules and constrains required by the competition. These are the key concepts leveraged in the algorithm, whose implementation will be described in later sections.

@@

Drools Planner\footnote{The Drools project, http://www.jboss.org/drools/} is an open-source Java-based solver that currently implements various tabu search techniques and simulated annealing. It allows for declaratively stating your problem, using the following basic concepts:

>>>>

\begin{abstract}
This article describes an entry to the \emph{2012 RAS Problem Solving Competition}, concerning dispatching on multi-track territories. The entry is based on the Drools Planner, a Java-based solver. On a reasonably recent computer, the resulting algorithm is able to produce feasible results within a minute and has been fine-tuned to provide best results in under 3 minutes. Source code of the entry is open and well documented.
\end{abstract}

@@

Working in the field of expert systems, tackling complicated problems can easily become one's hobby. But even in your spare time, you still want to find out how you compare to others. Having heard of the \emph{2012 RAS Problem Solving Competition} at that point, registering wasn't at all a tough decision. After spending many a night on it, this is what emerged.

We first describe the core concepts behind our submission, following by notes on the actual technical implementation. We show how the application can be used for both its primary purpose and also additional ones. We discuss the achieved results and potential for future improvement. In the appendices, we provide statistics for the best resolved systems.

Not being members of any of the Operations Research communities or even academia at all, we sincerely apologize to the reader of this paper for unknowingly not following any and all conventions for writing such documents. The seasoned researcher must be frightened by the complete lack of citations and sourcing~-- however, there is a simple explanation. We~used no literature whatsoever in our process, except for the occasional software documentation on-line.

@@

In this section, we describe the various approaches we have taken to implement the rules and constrains required by the competition. These are the key concepts leveraged in the algorithm, whose implementation will be described in later sections.

@@

Drools Planner\footnote{The Drools project, http://www.jboss.org/drools/} is an open-source Java-based solver that currently implements various tabu search techniques and simulated annealing. It allows for stating your problem in a declarative manner, using the following basic concepts:
